SAM simétrico y asimétrico

### 2021-04-30 analysis/scripts/paper_figs.Rmd
Agrega datos derivados
Closes #16

```{r compute-asymsam}
indexes_file <- data_path("derived", "indexes.Rds")
if (file.exists(indexes_file)) {
  indexes <- readRDS(indexes_file)
} else {
  stop("Run 02-compute-eofs.R")
}

>>>>

```{r compute-asymsam}
indexes_file <- data_path("derived", "indices.Rds")
if (file.exists(indexes_file)) {
  indexes <- readRDS(indexes_file)
} else {
  stop("Run 02-compute-eofs.R")
}
